### 2019-12-02 Mathematical Statistics/ms_ch_04.rmd
ms, ch4
ms, ch4

ggplot(data.table(x, y)) +
   geom_point(aes(x, y), color = "cornflowerblue", size = .6) +
   labs(title = "pdf f(x) = (3/8)*x**2")

@@

@@

@@

If $X_1, \ldots, X_n$ are i.i.d. from Unif[0, 1], how larage should n be so that $P(\bar{X} - \frac{1}{2} < 0.05) \ge 0.90$,

@@

>>>>

ggplot(data.table(x, y)) +
   geom_point(aes(x, y), color = "cornflowerblue", size = .6) +
   labs(title = paste("pdf: ", paste0(deparse(f), collapse = " ")))

@@

z <- ( 4.6 - 6 ) / ( 10 * sqrt(20) )

@@

```{r, echo = T, fig.height=3.5, fig.width=8}
pdf <- function(x) (3/16)*(x - 4)^2
x <- seq(from = 2, to = 6, by = 0.001)
y <- pdf(x)

ggplot(data.table(x,y)) +
   geom_point(aes(x, y), col = "cornflowerblue", lwd = .8) +
   labs(title = paste("PDF: ", paste0(deparse(f), collapse = " ")))

cdf <- function(x) (3/8)*(x - 4)

y <- cumsum(y) / sum(y)

ev <- x[min(which(y > .5))]

ggplot(data.table(x,y)) +
   geom_point(aes(x, y), col = "cornflowerblue", lwd = .8) +
   geom_vline(xintercept = ev) +
   labs(title = paste("CDF: ", paste0(deparse(f), collapse = " ")))

z <- ( 4.2 - ev ) / sqrt(244)
pnorm(z, lower.tail = F)

@@

If $X_1, \ldots, X_n$ are i.i.d. from Unif[0, 1], how large should n be so that $P(\bar{X} - \frac{1}{2} < 0.05) \ge 0.90$,

@@

### 4.16

Maria claims that she has drawn a random sample of size 30 from the exponential distribution with $\lambda = 1/10$.

The mean of her sample is 12.

a.) What is the expected value of a sample mean?

b.) Run a simulation by drawing 1000 random samples, each of size 30, from Exp(1/10), and compute the mean for each sample.

What proportion of the sample means is as large or larger than 12?

c.) Is a mean of 12 unusual for a sample of size 30 from Exp(1/10)?

### 4.17

Let $X \sim N(15, 3^2)$ and $Y \sim N(4, 2^2)$ be independent random variables.

a.) What is the exact sampling distribution of $W = X - 2Y$?

b.) Use R to simulate the sampling distribution of $W$ and plot your results.

Check that the simulated mean and standard error are close to the theoretical mean and standard error.

c.) Use the simulated sampling to estimate $P(W \le 10)$, and then check your estimate with an exact calculation.

### 4.18

Let $X \sim Pois(4)$, $Y \sim Pois(12)$, $U \sim Pois(3)$ be independent random variables.

a.) What is the exact sampling distribution of $W = X + Y + U$?

b.) Use R to simulate the sampling distribution of $W$ and plot your results.

Check that the simulated mean and standard error are close to the theoretical mean and standard error.

c.) Use the simulated sampling distribution to estimate $P(W \le 14)$ and then check your estimate with an exact calculation.

### 4.19

Let $X_1, X_2, \ldots, X_{10} \sim^{i.i.d} N(20, 8^2)$ and $Y_1, Y_2, \ldots, Y_{15} \sim^{i.i.d} N(16, 7^2)$.

Let $W = \bar{X} + \bar{Y}$

a.) Give the exact sampling distribution of W.

b.) Simulate the sampling distribution in R and plot your results. Check that the simulated mean and standard error are close to the exact mean and standard error.

c.) Use your simulation to find $P(W < 40)$. Calculate an exact answer and compare.
